\documentclass[a4paper]{article}
\usepackage[pdftex]{hyperref}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{xcolor}
% move the asterisk at the right position
\lstset{basicstyle=\ttfamily,tabsize=4,literate={*}{${}^*{}$}1}
%\lstset{language=C,basicstyle=\ttfamily}
\usepackage{moreverb}
\usepackage{palatino}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{comment}
\usepackage{verbatim}
\usepackage{color}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes.gates.logic.US,shapes.gates.logic.IEC,calc}

\usepackage[left=3cm, right=3cm, top=4cm, bottom=4cm]{geometry}

\usepackage{graphicx}

%% pdflatex?
\newif\ifpdf
\ifx\pdfoutput\undefined
\pdffalse % we are not running PDFLaTeX
\else
\pdfoutput=1 % we are running PDFLaTeX
\pdftrue
\fi
\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\ifpdf
\DeclareGraphicsExtensions{.pdf, .jpg}
\else
\DeclareGraphicsExtensions{.eps, .jpg}
\fi

\parindent=0cm
\parskip=0cm

\setlength{\columnseprule}{0.4pt}
\addtolength{\columnsep}{2pt}

\addtolength{\textheight}{5.5cm}
\addtolength{\topmargin}{-26mm}
\pagestyle{empty}

%%
%% Sheet setup
%% 
\newcommand{\coursename}{Computer Architecture and Programming Languages}
\newcommand{\courseno}{CO20-320241}
 
\newcommand{\sheettitle}{Homework}
\newcommand{\mytitle}{}
\newcommand{\mytoday}{December 5, 2018}

% Current Assignment number
\newcounter{assignmentno}
\setcounter{assignmentno}{11}

% Current Problem number, should always start at 1
\newcounter{problemno}
\setcounter{problemno}{1}

%%
%% problem and bonus environment
%%
\newcounter{probcalc}
\newcommand{\problem}[2]{
  \pagebreak[2]
  \setcounter{probcalc}{#2}
  ~\\
  {\large \textbf{Problem \arabic{assignmentno}.\arabic{problemno}} \hspace{0.2cm}\textit{#1}} \refstepcounter{problemno}\vspace{2pt}\\}

\newcommand{\bonus}[2]{
  \pagebreak[2]
  \setcounter{probcalc}{#2}
  ~\\
  {\large \textbf{Bonus Problem \arabic{assignmentno}.\arabic{problemno}} \hspace{0.2cm}\textit{#1}} \refstepcounter{problemno}\vspace{2pt}\\}

%% some counters  
\newcommand{\assignment}{\arabic{assignmentno}}

%% solution  
\newcommand{\solution}{\pagebreak[2]{\bf Solution:}\\}

%% Hyperref Setup
\hypersetup{pdftitle={Homework \assignment},
  pdfsubject={\coursename},
  pdfauthor={},
  pdfcreator={},
  pdfkeywords={Computer Architecture and Programming Languages},
  %  pdfpagemode={FullScreen},
  %colorlinks=true,
  %bookmarks=true,
  %hyperindex=true,
  bookmarksopen=false,
  bookmarksnumbered=true,
  breaklinks=true,
  %urlcolor=darkblue
  urlbordercolor={0 0 0.7}
}

\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{CStyle}{
    backgroundcolor=\color{backgroundColour},   
    commentstyle=\color{mGreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{mGray},
    stringstyle=\color{mPurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    language=C
}

\begin{document}
\coursename \hfill Course: \courseno\\
Jacobs University Bremen \hfill \mytoday\\
Dushan Terzikj\hfill
\vspace*{0.3cm}\\
\begin{center}
{\Large \sheettitle{} \assignment}\\
\end{center}

\problem{}{0}
\solution
In a single cycle approach we, the longest instruction is considered for timing each instruction. Therefore we have:\\ \\
$7\times 800=5600$\\ \\
For multicycle, all instructions will be executed at their corresponding time. Therefore we have:\\ \\
$2\times 800+700+3\times 600+500=4600$\\ \\
For pipeline approach, all instructions are happening concurrently. However, all instructions have a delay for the instruction fetch. That goes something like this:
\begin{center}
    \begin{tabular}{c|c|c|c|c}
        Instructions&&&&Total \\ \hline
        Load(800ps)&Store(700ps)&R-format(600)&Branch(500ps)&2600ps \\
        (Bubble)(800ps)&Load(800ps)&R-format(600)&&2200ps \\
        (Bubble)(800ps)&(Bubble)(800ps)&R-format(600)&&2200ps \\
    \end{tabular}
\end{center}
The largest value is 2600ps.
\begin{enumerate}[label=(\alph*)]
    \item $\frac{5600}{4600}=1.2173913$
    \item $\frac{5600}{2600}=2.15384615$
    \item $\frac{5600}{4600}=1.76923077$
\end{enumerate}
\textbf{CONTINUE HERE}

\problem{}{0}
\solution
Bold characters are not included in the regex. Some expressions have two solutions. The reason for this is that the table does not contain or it conflicts some knowledge about regexes I know from before. In order to check that out go to \underline{\textcolor{blue}{\href{https://regexr.com/}{regexr}}}.
\begin{enumerate}
    \item[(a)] "\textbackslash{\$}zero" \\ \textbf{OR} \\ (zero)
    \item[(b)] \textbackslash{a}[a-zA-Z0-9]*\textbackslash{b} \\ \textbf{OR} \\ a[a-zA-Z0-9]*b
    \item[(c)] [0-9][a-zA-Z0-9\_]*[0-9]
    \item[(d)] "abb"a\{4\}[ab]\{0,3\} \\ \textbf{OR} \\ (abb)a\{4\}[ab]\{0,3\}
    \item[(e)] [1-9]+[0-9]*
    \item[(f)] [-]?[1-9]+[0-9]*
    \item[(g)] [0-9]*[.]?[0-9]*
    \item[(h)] $(\text{pit}|\text{spot}|\text{spate}|\text{slap two}|\text{respite})$
\end{enumerate}
\newpage
\problem{}{0}
\solution
\begin{enumerate}
    \item (1) and (3)
    \item All of them except (5)
    \item (3) (4) (5)
    \item All except (4)
\end{enumerate}

\end{document}